Human tissue specific markers

### 2017-06-08 manuscript/manuscript.Rnw
include plot of housekeeping tissue specific markers

>>>>

\subsubsection{Genes which are housekeeping and specific}

\DLA{Why are these two genes housekeeping and specific?}

\begin{figure}
<<housekeeping_tissue_specific_markers_figure,fig.width=4,fig.height=4,echo=FALSE>>=
print(specific.markers.barplot(genes=c("MT-TM","C19orf28"))
      + xlab("Housekeeping Tissue\nSpecific Genes")
      + theme(legend.position="Top")
      + ylab("Tissue"))
@
\caption{Genes which are tissue specific but are also housekeeping genes}
\label{fig:housekeeping_tissue_specific_genes}
\end{figure}
